Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-12-29 manuscript/manuscript.tex
Edit the computational performance section
Rename it to Algorithm Performance. Not much is changed here, just some
re-wording.

\section{Computation time comparison}

Because the density-based algorithm produces discretizations along the radial direction,
besides the latitudinal and longitudinal ones generated by the two dimensional adaptive
one, the computation time of the gravitational fields of variable density tesseroids
will be increased in comparison to the homogeneous density case.
In order to quantize this increase we perform a computation time comparison between the
homogeneous density case with the linear and the exponential ones.

We define a $20^\circ \times 20^\circ$ tesseroid of 1km of thickness and a single
computation point located at different heights (1m, 10m, 100m, 1km, 10km, 100km and
1000km) above the top surface of the tesseroid.
Then we compute the gravitational potential $V$ and the $g_z$ that the tesseroid
generates on the computation point in case of an homogeneous density, a linear density
and an exponential density with $b = 3$ (Eq.~\ref{eq:density-exp}).
We perform 1000 computations for each field, density and computation height while
tracking the computation time for each one of them.
The final computation time is obtained as the mean value of these runs.

Fig.~\ref{fig:computation-times} shows the computation time ratio between the
computations times of the linear and exponential density with the one for an homogeneous
density, defined as:

\begin{equation}
    \text{Computation time ratio} = \frac{\Delta t}{\Delta t_\text{homog}},
\end{equation}

\noindent where $\Delta t_\text{homog}$ is the computation time for the homogeneous
density and $\Delta t$ is the computation time for the linear or the exponential
density.

>>>>

\section{Algorithm performance}

Because the density-based discretization algorithm introduces more division along the
radial dimension, it is reasonable that the computation time for variable densities will
be increased in comparison to the homogeneous density case.
In addition to the extra division, there is also the overhead imposed by the extra
function calls to evaluate the density function.
In order to quantify these effects, compare the computation times between the
homogeneous density case and the linear and the exponential density ones.
We note that these results are highly dependent on our particular implementation of the
algorithm and choice of programming language.

We define a $20^\circ \times 20^\circ$ tesseroid of 1 km of thickness and a single
computation point located at different heights above the top surface of the tesseroid (1
m, 10 m, 100 m, 1 km, 10 km, 100 km and 1000 km).
We then compute $V$ and $g_z$ for the homogeneous, linear, and exponential (with $b =
3$) density cases.
We perform 1000 computations for each field, density function, and height while tracking
their computation time.
The final computation time is the mean of these 1000 executions.

Fig.~\ref{fig:computation-times} shows the computation times relative to the homogeneous
case (i.e., ${\Delta t}/{\Delta t_\text{homog}}$).
